You are allowed to use two sheets of notes. 

Multiple choice are worth 1 pt, short answer questions are worth more. I recommend you quickly read through the multiple choice questions and use the information contained within them to aid you in answering the essay questions, but do not spend excessive time answering the multiple choice. If time permits, please answer all before turning in your test to maximize your score.

In answering the short answer questions, be thorough but concise. Deep understanding of the concepts will be displayed by proper use of vocabulary and discussion of the interconnectedness of concepts.

For earned honors, be sure to address all listed points in the short answer questions.




Refer to the phylogenetic tree of life above. Which statement is consistent with the tree? 
The most recent common ancestor of chordates and echinoderms had deuterostomic development (second hole becomes mouth) as a shared, derived trait.
The most recent common ancestor of chordates and echinoderms shed their skin as a shared, derived trait.
The most recent common ancestor of chordates and echinoderms shared radial symmetry and neuromuscular cells as a shared, derived trait. 
Chordates and echinoderms do not share a common ancestor. 



Which of the following statements regarding evolution is FALSE
Evolution does not have a "drive" and does not always act to improve one particular function
Evolution is descent with modification
Evolution does not require having heritable traits nor differential survival of offspring
Evolution can occur rapidly or over geologic timescales




Which of the following are examples of scientific evidence that life on earth has been around for a long time (3.9 billion years in case of prokaryotes, 550 million years in case of multicellular life). Please mark all that apply. 
Fossil bacteria in rocks that are 2-4 billion years old
Sea creatures in rocks that have been raised to the top of the Andes due to geologic processes
Molecular divergence times for animals of about 600 million years before present; and for prokaryotes of 2-4 billion years before present
Written genealogies (family histories for historical or mythical people) stretching back 4000-5000 years before present. 




Which of the following is true about the molecule best described as the "energy currency" of the cell
Adenosine triphosphate can be broken into adenosine diphosphate and a phosphate group, releasing energy
The enzyme adenosinase removes adenosine from adenosine diphosphate and grafts it onto adenosine triphosphate, storing energy for later release
In adenosine triphosphate, the three phosphate groups are able to store energy because they are like unstable, boisterous 8th graders forced to sit on the same, too small bus bench seat; when a phosphate is removed, energy is thus released
Adenosine triphosphate can be synthesized from adenosine diphosphate by means of ATP synthase, an enzyme resident in the membranes of mitochondria and chlorplast that is powered by a proton 




Which of the following about classification and taxonomy are true? Select all that apply
Example phyla include porifera (sponges), cnidaria (anemones, jellyfish), mollusks, arthropods, and chordates 
Species and genus are typically written in that order, as in ergaster Homo, mola Mola, gorilla Gorilla, pelagica Chaetura
While taxonomic ranks are well entrenched in biology textbooks and standardized tests, a criticism of them is that the ranks are not necessarily equivalent among groups, e.g. a "class" among vertebrates is not necessarily the same tree level as in insects or worms
Valid named groups (such as mammals and birds) that include all the living relatives of a single common ancestory are referred to as monophyletic and crown groups; other groups that leave things out (such as "reptiles") are called paraphyletic and are placed in quotes. 





Which of the following is NOT consistent with the flow of energy in an ecosystem
Because cellular energetic processes are 100% efficient, we expect to see equal biomass of primary producers, grazers, and predators
In terrestrial ecosystems, we expect to see the highest biomass of primary producers, then grazers, then the least biomass will be predators. 
Cellular energetic processes can shape global climate and drastically affect the abundance and distribution of life at the ecosystem level
While most energy comes from the sun, there are ecosystems on earth that utilize alternative sources of energy




Which of the following are ways a single cell can bend the limits of diffusion
Being large in one dimension but being skinny in other dimensions
Using ATP to power membrane spanning protiens to actively pump materials against concentration gradients
Using special organelles or increasing flow to improve intake or output of materials
By growing very large, cells can avoid the need to rely on diffusion





Which of the following about cellular respiration is FALSE? 
The Citric Acid Cycle is also named the Krebs Cycle, after Hans Krebs, who was eventually awarded the Nobel Prize for his work. 
Glycolysis does not require oxygen to proceed. 
Overall, cellular respiration uses energy from photons to synthesize CO2 and water into glucose, liberating oxygen. 
The mitochondrion is the site of cellular respiration, and includes inner membranes that provide the site for the enzymes used in the process as well as allowing for a proton gradient to power ATP production. 





When we made gravlax, we discussed salmon as an example of an anadromous fish that moves between freshwater and saltwater (and back). Why is this physiologically challenging? 
In seawater, the water is hypotonic to the fish and causes it to intake excess water
In seawater, the water is hypertonic to the fish and causes it to intake excess water
In freshwater, the water is hypotonic to the fish and causes it to intake excess water
In freshwater, the water is hypertonic to the fish and causes it to intake excess water





Which of the following about the history of animal life on earth is TRUE? 
Once an animal group comes ashore, they never return to the water
Unrelated animal groups never evolve similar looking features
Once a complex feature is evolved, it is never lost
Animal life appears to have appeared and diversified into all of the known phyla within a relatively short 




A Rube Goldberg machine is an overly complicated contraption that accomplishes a simple task using repurposed stuff. Consider both photosynthesis and respiration, and explain whether you think an analogy to a Rube Golderberg machine applies. Is your chosen process "well designed"? Hypothesize if the steps could have been borrowed from, or are similar to, other processes, and what you think this means.  For earned honors, please identify specific sub-processes that could work on their own within other (e.g. anaerobic) processes and identify specific molecular hardware that appears to be co-opted or exapted from other uses. 

This week, instead of making gravlax you decide to make kimchi (Korean fermented cabbage). As the first step, the cabbage is placed in a salty solution. As the last step, the cabbage is placed in a sealed container. The final product smells sour. Explain the first step and the last step, using what you know about biology. For earned honors, specifically, please explain what type of solution the salt bath is and what specific effect it should have on the cabbage. Also please explain what placement in a sealed container does, specifically referencing cellular biochemical processes. 

A little bit of energy is emitted by the sun. It falls to earth, is captured by a banana tree, turned into a banana, that is then eaten by an MBS student who then wins a hockey game. Tell a story about this bit of energy and how it is incorporated into, and transforms among, biomolecules to power the game winning goal shot. For earned honors, please try to include specific chemical reactions, diagrams explaining structures at the cellular and organism level, etc. 

Pick the most noteworthy thing you've heard about an animal or plant this term, explain what you know about the biology, and explain why you think it is interesting. For earned honors, please address both proximate and ultimate causes (after Tinbergen), i.e. please address both the proximate biochemical or organism physiological processes as well as factors related to the evolution or ecology of your topic. 