\documentclass{article}

\usepackage[authoryear,round]{natbib}
\usepackage{bibentry}
\bibliographystyle{apalike}
\nobibliography{*}
\usepackage[colorlinks=true]{hyperref}
\usepackage{booktabs}

\title{Biology 11 Syllabus}
\author{Dennis Evangelista}
\date{\today}

\begin{document}
%\maketitle

\begin{enumerate}
\item \textbf{Course outline.} Throughout this course, students will gain a scientific understanding of life and the laws, theories and principles that govern it. This will be accomplished by exploring concepts in biology and examining the history and nature of science. Concepts are presented in a conceptual approach, showing how the topics are connected to each other and allowing students to build on what they already know. Students will learn the major and guiding principles of molecular and cellular biology and how they work together to control the functions of all living things. Evolution is considered one of the guiding principles and will be incorporated into the content throughout the year, aiding students in making connections between the various concepts. The content discussed in this course includes:
\begin{enumerate}
\item Uncertainty and nature of science
\item Characteristics of life
\item Chemistry of life
\item Molecular genetics
\item Mendelian genetics
\item Cellular structure and function
\item Cellular energy
\item Ecology
\end{enumerate}

\item \textbf{Class materials.} The following materials are required for class. Students are encouraged to take their notes using their iPad or laptop, but may use a notebook or binder if he/she chooses.
\begin{enumerate}
\item iPad/Laptop, with the following required apps:
\begin{enumerate}
\item Google Classroom for distribution of course materials
%\item Notability
\item iWork Suite, Microsoft Office, or Ubuntu/\LaTeX/Python. 
\item Zoom, for online meetings
\item Go Formative, for online tests/quizzes/exams.
\end{enumerate}
\item Textbook: \bibentry{fowler2017concepts}. A free online version can be found at \url{https://openstax.org/details/books/concepts-biology}.
\end{enumerate}

\item \textbf{Grading breakdown.}
\begin{table}[h]
\begin{center}
\begin{tabular}{ll}
\toprule
Tests & 20\% \\
Quizzes & 20\% \\
Projects and essays & 20\% \\
Laboratory participation \& reports & 20\% \\
Homework & 10\% \\
Engagement, growth \& curiosity & 10\% \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\item \textbf{Class meetings.} The course will meet either 2 or 3 times a week, depending on the A or B week schedule. If you are attending class virtually, classes can be accessed using the following Zoom link: \url{https://zoom.us.my/popielski}

\item \textbf{Class websits, uses, and expectations.}
There are three major Google applications that are associated with this, and all courses at MBS.
\begin{enumerate}
\item Both sections of Biology (periods 5 and 8) will use the same Google Site. The link to the Google Site can be found at \url{https://sites.google.com/mbs.net/popielski/home}. The Google Site will be used throughout the year and is a good spot to locate information and additional resources for this course.  The site also includes Mrs. Popielski’s teaching schedule and availability.
\item Each section of the class has its own Google Classroom and associated Google Calendar.
\item All assignments will be posted on Google Calendar and be available through Google Classroom.
\end{enumerate}

\item \textbf{Earned honors in Biology.} Throughout the course, students will have the option earn honors in Biology. General expectations for both the Standard and Honors students are included on the Google Classroom and Google Site for this course. Additionally, you can access the information here. For each unit and/or assessment, differentiated opportunities will be explained in more detail through the learning goals of specific units.

\item \textbf{Homework and assignment policy.} 
\begin{enumerate}
\item All assignments for this class will be available on Google Classroom along with any important information and due dates.
\item All due dates for assignments will be posted on Google Calendar, linked with Google Classroom.
\item All homework is due the class after it was assigned, unless otherwise stated by the teacher and Google Calendar.
\item Missing homework will result in zero points earned until the assignment is turned in by the student.
\item Late homework, labs or projects will be accepted but will result in a 10\% credit deduction for every school day that it is late.
\item If an assignment is turned in late due to an excused absence, it will not receive point deductions.
\item Excused absences include pre-scheduled college visits and any other days considered to be excused as per the school policy.
\item In case of an absence, it is the student’s responsibility to obtain any notes, work and assignments.
\item Assignments missed because of an absence need to be made up as soon as possible. If a quiz or test was missed due to an absence, students should schedule a time with the instructor to make-up the assessment either: before/after school, during a free period or during collaborative period.
\item If a student is struggling with material that was covered while he/she was out of class, they can receive extra help during collaborative period or by scheduling a time to meet before/after school or during a free period.
\end{enumerate}

\item \textbf{Quizzes and tests.} 
\begin{enumerate}
\item Go Formative, an online testing platform used by many teachers at MBS, will be used to administer tests and quizzes.
\item Prior to each test, students will be given a study guide as well as sample questions to help them prepare.
\item For each quiz, students will have the opportunity to complete an optional correction sheet to earn back half credit on any questions marked incorrect. Quiz corrections should be used as a learning experience to help students prepare for upcoming tests.
\item On tests, students can complete corrections for all scores below an 80\%.
\item Test/quiz corrections must be submitted along with the original graded assessment.
\item Students will have one week after receiving their graded assessment to successfully complete any corrections.
\end{enumerate}

\item \textbf{Classroom rules and policies.} Below are a general list of classroom rules and procedures that shall be followed at all times. Students will receive more specific guidelines, and a separate contract, on Laboratory Rules
and Procedures.
\begin{enumerate}
\item Students should behave and dress according to the school guidelines outlined in the MBS Student and Parent Handbook.
\item Arrive to class on time, prepared with all materials, assignments or projects.
\item Behavior should promote learning and inquire and not disrupt it.
\item All behavior and discussion in class is should be respectful of all members of the learning community.
\item On lab days, students are expected to dress in accordance to the safety guidelines that will be discussed in class (e.g. no open-toe shoes).
\item Laboratory rules and expectations must be followed at all times during lab.
\item In class, all technology should be used for the advancement the learning process (taking notes, virtual labs, educational resources, etc.)
\item No form of academic dishonesty or plagiarism will be tolerated. Because there is often a lot of collaboration and group work in science, students should turn in their own assignments, in their own words, unless told otherwise by the instructor.
\item Failure to follow any of the classroom rules will result in a verbal warning the first time a rule is broken.
\item Failure to correct the problem will result a parent/guardian contact through the school’s electronic PCF system. 
\item Any severe disruptions will immediately be brought to the attention of both school administration and guardians. Severe disruptions are considered to be: overt refusal to follow instructions, fighting, vandalism and any behavior that threatens/disrupts the safety of students, the learning environment and the school.
\end{enumerate}

\item \textbf{Instructor contact information.}
\begin{table}[h]
\hspace{3in}
\begin{tabular}{l}
Dr. Evangelista \\
Science Department Faculty \\
MSC xxx \\
E-mail: \emph{devangelista@mbs.net} \\ 
School Phone: (973) 539-3032 ext. 864 \\
\end{tabular}
\end{table}

\end{enumerate}

\nocite{fowler2017concepts}
\nobibliography{biology11.bib}
\end{document}