This document is an organized checklist of work to complete and to monitor your progress through this self-paced unit. The Handout contains all the same links given here along with specific instructions for each part of the unit. You can work with a partner or partners on these assignments, however, it is STRONGLY recommended that you do your own reading, video watching, note taking, and completing of the table in order to understand the material. The quizzes, Google Forms, gif, and test will be completed individually. You have until the night before your section’s test on this unit to hand in any graded assessments. This document may be updated throughout the unit.


Items to Complete
	Instructions
	Introduction to the unit
	

	1. Lecture: Introduction to cellular energetics
	Use the slides to take notes and to later review the material in the textbook
	1. Textbook section 4.1 
	This is the material that the lecture is based on and you may need to read it to get the main concepts
	1. Redox video
	Watching this video and taking notes is highly recommended before starting the unit
	Part I: ATP and Glycolysis
	

	1. Cellular Respiration Table
	While you are reading and doing the activities in this unit, use this document to summarize the main components. You will be allowed to use this table on the test for this unit
	2. Read and take notes on textbook section 4.2
	Use the vocabulary and important concepts listed on the handout for guidance and pay attention to diagrams
	3. POGIL Part I
	You do not need to turn this in, but do need to complete this Google Form with selected answers from the POGIL for grading
	4. Quiz I: ATP and Glycolysis
	This is a closed notes quiz worth ____ points that is based on the reading and concepts from the POGIL. It will focus mainly on ATP, the general concept of cellular energy, and glycolysis. You can take it at any point during the unit.
	Part II: Citric Acid Cycle and Oxidative Phosphorylation 
	

	5. Read and take notes on textbook section 4.3
	Use the vocabulary and important concepts listed on the handout for guidance and pay attention to diagrams
	6. POGIL Part II
	

	7. Quiz II: Citric Acid Cycle and Oxidative Phosphorylation
	

	Part III: Fermentation
	

	8. Read and take notes on textbook section 4.4
	Use the vocabulary and important concepts listed on the handout for guidance and pay attention to diagrams
	9. POGIL Part III
	

	10. Quiz III: 
	

	Part IV: Putting it all together
	

	Lab-ish: Cellular Respiration Case Study
	You will need to submit a document with typed responses for the questions in the case study
	Project: Create a GIF for either Glycolysis, the Citric Acid Cycle, or Oxidative Phosphorylation
	

	Part V: Comparison of Photosynthesis and Cellular Respiration
	

	Gif Critiques
	While you were working through cellular respiration, your classmates were studying photosynthesis. You will now get to critique three gifs in order to compare and contrast them to what you have learned.
	Unit 4 Test
	This test will be a shortened version of the usual test format with 10 multiple choice questions and 2 or 3 essay questions